Deriving Multi-headed Planar Dependency Parses from Link Grammar Parses

### 2014-05-19 doc/LinksToDAG.tex
Added tikz-dependency to the paper. I want to be able to generate dependency graphs to see. The paper will read off exampleSentence.tikz and paste it into its example sentence category.

@@

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{soul}
\newcommand{\Note}[1]{}
\renewcommand{\Note}[1]{\hl{[#1]}}  % comment out this definition to suppress all Notes                                                                                
\newcommand{\TODO}[1]{\Note{TODO: #1}}
\newcommand{\NoteSigned}[3]{{\sethlcolor{#2}\Note{#1: #3}}}
\newcommand{\NoteJE}[1]{\NoteSigned{JE}{LightBlue}{#1}}
\newcommand{\NoteJH}[1]{\NoteSigned{JH}{YellowGreen}{#1}}

@@

@@

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{soul}

@@

\usepackage{tikz-dependency}

\newcommand{\Note}[1]{}
\renewcommand{\Note}[1]{\hl{[#1]}}  % comment out this definition to suppress all Notes                                                                                
\newcommand{\TODO}[1]{\Note{TODO: #1}}
\newcommand{\NoteSigned}[3]{{\sethlcolor{#2}\Note{#1: #3}}}
\newcommand{\NoteJE}[1]{\NoteSigned{JE}{LightBlue}{#1}}
\newcommand{\NoteJH}[1]{\NoteSigned{JH}{YellowGreen}{#1}}

@@

\begin{equation}
  count_{L, left} = \sum_{a \in ARCS with label L} left_a
\end{equation}
\begin{equation}
  count_{L, left} = M * allowed_{L,left} + slack_{L}
\end{equation}
Where $L \in LABELS$, and $M$ is the size of the corpus.
The objective is:
\begin{equation}
  \min \sum_{L \in LABELS \atop DIR \in \{left, right\}} (allowed_{L,DIR}) \atop + COST(L) * \sum_L slack_L
\end{equation}
\begin{equation}
  COST(L) = \frac{100}{(count_{L,left} + count_{L,right})}
\end{equation}

@@

\begin{figure}[ht!]
  \centering
  \input{figure/exampleSentence.tikz}
  \caption{Example}
\end{figure}
